\normalfont \normalsize \textsc{UNSW School of Computer Science and Engineering} \\ [24pt] \horrule{1pt} \\[0.5cm] \LARGE Word Embedding and Question Answering \\ \horrule{1pt} \\[0.5cm]

### 2019-12-11 paper.tex
autoencoder done

\begin{figure}
  \includegraphics[width=\linewidth]{nnlm.png}
  \caption{Figure 4: Neural Network Based Mapping}
  \label{fig:nnlm}
\end{figure}
\subsubsection{Autoencoder (GAN)}
An autoencoder is a type of neural network that learns to label dimensions in an unsupervised manner. Figure 5 shows that an autoencoder is composed of two parts: the input side, marked as $X$, and the reconstruction (output) side, marked as $X'$. The $X$ tries to learn a distributed representation of the original data that aims to reduce the dimensions, and the $X'$ side is where the autoencoder tries to generate from the reduced representation as close as possible to its original input, hence its name, reconstruction. 
\begin{figure}
  \includegraphics[width=\linewidth]{Autoencoder_structure.png}
  \caption{Figure 5: Schematic structure of an autoencoder with 3 fully connected hidden layers. The code (z, or h for reference in the text) is the most internal layer.}
  \label{fig:autoencoder}
\end{figure}
\paragraph{Basic Architecture of Autoencoder}
An autoencoder consists of two parts, the encoder and the decoder, which can be defined as transitions $\psi$ and $\phi$, such that:
\begin{align*}
& \psi : \chi \mapsto \mathfrak{F} \\
& \phi : \mathfrak{F} \mapsto \chi \\
& \psi, \phi = arg_{\psi, \phi} min \lvert \chi - (\psi * \phi) \chi \rvert
\end{align*}
In the simplest form, we assume there is only one hidden layer. The encoder stage of the autoencoder takes input $x \in \mathbb{R}^{d} = \chi$ and maps it to $\mathbf{h} \in \mathbb{R}^{p} = \mathfrak{F}$. \\
\begin{align*}
\mathbf{h} = \delta (\mathbf{W}x + \mathbf{b})
\end{align*}
This image $\mathbf{h}$ is the code section shown in Figure 5. $\delta$ is normally a sigmoid function defined as following: \\
\begin{align*}
S(x) = \frac{1}{1 + e^{-x}} = \frac{e^x}{e^x + 1}
\end{align*}
$\mathbf{W}$ is a weight matrix and $\mathbf{b}$ is a bias vector. The initializations of these two variables are random. They will be learnt iteratively through \textbf{backpropagation}. \\

\subsubsection{Neural Network Language Model (NNLM)}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{nnlm.png}
  \caption{Figure 4: Neural Network Based Mapping}
  \label{fig:nnlm}
\end{figure}
\subsubsection{Autoencoder (GAN)}
An autoencoder is a type of neural network that learns to label dimensions in an unsupervised manner. Figure 5 shows that an autoencoder is composed of two parts: the input side, marked as $X$, and the reconstruction (output) side, marked as $X'$. The $X$ tries to learn a distributed representation of the original data that aims to reduce the dimensions, and the $X'$ side is where the autoencoder tries to generate from the reduced representation as close as possible to its original input, hence its name, reconstruction. 
\begin{figure}
  \includegraphics[width=\linewidth]{Autoencoder_structure.png}
  \caption{Figure 5: Schematic structure of an autoencoder with 3 fully connected hidden layers. The code (z, or h for reference in the text) is the most internal layer.}
  \label{fig:autoencoder}
\end{figure}
\paragraph{Basic Architecture of Autoencoder}
An autoencoder consists of two parts, the encoder and the decoder, which can be defined as transitions $\psi$ and $\phi$, such that:
\begin{align*}
& \psi : \chi \mapsto \mathfrak{F} \\
& \phi : \mathfrak{F} \mapsto \chi \\
& \psi, \phi = arg_{\psi, \phi} min \lvert \chi - (\psi * \phi) \chi \rvert
\end{align*}
In the simplest form, we assume there is only one hidden layer. The encoder stage of the autoencoder takes input $x \in \mathbb{R}^{d} = \chi$ and maps it to $\mathbf{h} \in \mathbb{R}^{p} = \mathfrak{F}$. \\
\begin{align*}
\mathbf{h} = \delta (\mathbf{W}x + \mathbf{b})
\end{align*}
This image $\mathbf{h}$ is the code section shown in Figure 5. $\delta$ is normally a sigmoid function defined as following: \\
\begin{align*}
S(x) = \frac{1}{1 + e^{-x}} = \frac{e^x}{e^x + 1}
\end{align*}
$\mathbf{W}$ is a weight matrix and $\mathbf{b}$ is a bias vector. The initializations of these two variables are random. They will be learnt iteratively through \textbf{backpropagation}. \\
\begin{align*}
\mathbf{h'} = \sigma (\mathbf{W'}x + \mathbf{b'})
\end{align*}
The backpropagation computes weight space $\mathbf{W}$ and bias vector $b$ with respect of a loss function $\mathbb{C}$.\\\\
$x$ : input (vector of features). \\
$x'$ : target output, the closer to $x$, the better. \\
$\mathbb{C}$: loss function, which intuitively associate with the "cost" of certain event or representation. The aim of training is to minimize the loss function. \\
$L$: the number of layers. In the above example, L equals to 1. However, here we aims to provide a generalized form.\\
$W^l = W^l_{j_k}$: the weights between layer  $l-1$ and $l$, where $W^l_{j_k}$ is the weight between the k-th node in layer $l$-1 and the $j$-th node in layer $l$.\\
$f^l$: sigmoid function at layer $l$.\\
The whole neural network can be represented by this function:\\
\begin{align*}
g(x) = f^{L}(W^Lf^{L-1}(W^{L-1}...f^1(W^1*x)...)
\end{align*}
For each input $x_i$, there will be an output $x'_i$ corresponding with it. the loss of the model on that pair is the cost of the difference between the predicted output $g(x_i)$  and the target output $x'_i$:\\
\begin{align*}
\mathbb{C}(y_i, f^{L}(W^Lf^{L-1}(W^{L-1}...f^1(W^1*x)...))
\end{align*}
For each layer, we compute the minimum of the loss function by calculating its derivatives. 
\begin{align*}
\frac{\partial \mathbb{C}}{\partial W^l_{j_k}}
\end{align*}
Where the loss function is defined as: 
\begin{align*}
\mathbb{C}(x, x') = \lvert x - x'\rvert^2 = \lvert x - \sigma'(\mathbf{W}'(\sigma (\mathbf{W}x + b)) + b' \rvert
\end{align*}
where $x$ is the average across all inputs.
\subsubsection{Neural Network Language Model (NNLM)}
